An object deserves more than a single name

### 2018-12-20 papers/ACL2019/acl19_naming.tex
progress in intro

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
\newcommand{\das}[1]{\textcolor{red}{\emph{//das: #1//}}}
\newcommand{\refexp}[1]{\textsl{#1}}
\newcommand{\word}[1]{\textsl{#1}}
\newcommand{\cat}[1]{\textsc{#1}}

@@

Categorizing and naming real-world objects is a fundamental ability of human cognition and communication. In NLP, object naming is a core phenomenon which is part of virtually every Language \& Vision task.
Since objects are often simultaneously a member of multiple categories (e.g., a young \refexp{beagle} is at once a \cat{dog}, a \cat{beagle}, an \cat{animal}, a \cat{puppy} etc.), the act of naming an object amounts to that of selecting a lexical concept  for it among the various potential alternatives.

Research on categorization and language production has used object naming as a basic paradigm for investigating the processes that underly formation, organization and retrieval of concepts in the human mind  \cite{rosch1976basic} \sz{cite more here}.
Research in computer vision has focused on automatic object recognition where, recently, powerful models have been developed that classify visual objects in real-world images into thousands of different categories \newcite{googlenet}.
In NLP (L\&V), however, research on object naming is relatively scarce.
While there has been an explosion of interest in various, sometimes complex, L\&V tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}, there has hardly been any work looking at linguistic questions involved in object naming.
As the starting point of this work, we argue that existing resources in L\&V constitute an excellent basis for empirical, large-scale investigations into object naming.
At the same time, we show that we need to systematically extend them and collect naming data in a more ??? way, so as to arrive at a solid empirical approach.

Shortcomings of existing resources:

\begin{itemize}
\item most corpora record a single label or a small set of descriptions for each object
\item no systematic inventory of object labels
\item existing taxonomies (WordNet) are not really useful
\end{itemize}

@@

@@

\bibliography{ontowac}
\bibliographystyle{acl_natbib}

>>>>

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
\newcommand{\das}[1]{\textcolor{red}{\emph{//das: #1//}}}
\newcommand{\refexp}[1]{\textsl{#1}}
\newcommand{\word}[1]{\textsl{#1}}
\newcommand{\cat}[1]{\textsc{#1}}
\newcommand{\vgenome}{VisualGenome\xspace}

@@

The real-world objects that we interact with in our every-day life can be categorized into many thousands and maybe millions of different categories. And even a single object can be member of many categories, i.e.\ at different taxonomical levels or in different parts of a taxonomy. For instance, the object in Figure \ref{fig:cake} is at once a \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc.

\begin{figure}[htbp]
\begin{center}
\includegraphics[height=2cm,width=2.5cm]{Figures/cheescake.png}
\caption{A real-world object in VisualGenome}
\label{fig:cake}
\end{center}
\end{figure}

Given the abundance of concepts available in language, the act of \textit{naming} a visual object is less trivial than it might seem intuitively: in order to describe or refer to an object, a name has to be selected from a complex network of concepts and from many competing lexical alternatives.
Hence, research on cognition and language production has relied on object naming as a basic paradigm for investigating the processes that underly formation and organization of concepts in the human mind  \cite{rosch1976basic} \sz{cite more here}, though mostly using idealized, graphical objects from specific domains (plants, animals) as visual stimuli.
Complementary to that, research in computer vision has (successfully) focused on automatically recognizing \textit{real-world} objects in images or videos, but using simplified categorization schemes where each object is assigned a single correct label or name, cf.\ \cite{googlenet}. %Here, powerful models have been developed recently that classify visual objects in real-world images into thousands of different (mutually exclusive) categories \newcite{googlenet}.

In NLP, to date, research on object naming is relatively scarce despite the fact that
 there has been a recent explosion of interest in various, and even complex, language \& vision tasks ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic} to e.g.\ visual dialogue \cite{das2017visual,vries2017guesswhat}.
In this paper, we argue that a lot of research in this area would benefit from a deeper and more systematic understanding of the semantic and taxonomic processes in object naming, which is a core phenomenon in virtually every vision \& language task.
At the same time, we argue that existing resources in L\&V constitute an excellent, large-scale test bed for assessing traditional claims and theories such as, e.g.\ the existence of so-called entry-level categories  \cite{rosch1976basic}.

The goal of this paper is to extend some existing, large-scale resources available for language \& vision research in a way that they can serve as a solid and broad empirical basis for investigations into object naming. 
Thus, while large amounts images from different domains paired with verbal descriptions are generally available, none of the existing corpora records more than a few annotations per object.
Even VisualGenome \cite{krishna2016visualgenome}, one of the most exhaustively annotated resources to date, only provides a single, manually annotated object description (including a single name) per object. 
Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g. object labels are typically quite general as in Flickr30k \cite{plummer2015flickr30kentities} (e.g.,~\cat{people, animals, bodyparts, clothing}) or taxonomically heterogeneous as in MS COCO \cite{mscoco} (e.g.,~\cat{people, baseball glove, bird}).
These two shortcomings - few names per object and inconsistent labeling of categories - make it difficult to get reliable and stable predictions as to how speakers will likely name a given object.\sz{need to make this point more clear}

@@

\paragraph{Existing resources and their shortcomings} summarize SIVL paper here

@@

\bibliography{naming}
\bibliographystyle{acl_natbib}
